Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2023-10-01 paper.Rmd
Fixed plotting issue

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
# csl: apa.csl
# bibliography: regrep.bib
---

@@

source('draft_analysis.R')
```
EHB Registered Report

@@

Figure1 <- forestplot(
  m_agefirst,
  m_lifetime,
  m_pastyear,
  m_partnered,
  intercept = F,
  facet = F,
  dodgewidth = .5,
  modelnames = mnames1,
  varnames = vnames, 
  size = 1.2, 
  linewidth = 1
) + theme_minimal(17) +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .5)) +
#  labs(title = "Figure 1. Baseline Models: Regression coefficients from generalized linear models", color = "Model") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
# 
# 
# annotate_figure(fig1,
#                            top = text_grob("Figure 1. Baseline Models: Regression coefficients from generalized linear models\n",
#                                            size = 20, face = "bold",
#                                            hjust = 0,
#                                            x = 0.01),
#                            bottom = text_grob("Variables labelled (S) have been centered at the mean and standarized by 2 SD",
#                                               size = 12))

@@

fig1 <- forestplot(
   msoc1, mheal1, mphys1, mhor1,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames, 
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) + theme_minimal() +
  theme(axis.text.y = element_text(size = 9), plot.title = element_text(size = 11)) +
 # geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Lifetime Number of Sexual Partners") 
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig2 <- forestplot(
 msoc2,mheal2, mphys2, mhor2,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
 size = 0.7, 
  linewidth = 0.7
) + theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(.8)) +
  labs(title = "Past Year Number of Sexual Partners")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig3 <- forestplot(
  msoc3, mheal3, mphys3, mhor3,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) +
  theme_minimal() +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .7)) +
  labs(title = "Age at First Sex")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
 # coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

fig4 <- forestplot(
  msoc4, mheal4, mphys4, mhor4,
  intercept = F,
  facet = F,
  dodgewidth = .8,
  modelnames = mnames,
  varnames = vnames, 
  size = 0.7, 
  linewidth = 0.7) +
  theme_minimal() + 
  #geom_pointrange(size = 1.2, position = position_dodge(width = .8)) +
  labs(title = "Currently Partnered")  +
  theme(axis.text.y = element_blank(), plot.title = element_text(size = 11))
#  coord_cartesian(clip = "off")
# + xlim(-2.5, 3.55)

@@

# ggarrange(fig1, fig2, fig3, fig4,
#                      labels = "AUTO",
#                      font.label = list(size = 20),
#                      ncol = 2, nrow = 2,
#                      common.legend = TRUE, legend="bottom")

 # annotate_figure(fig1234,
 #                       top = text_grob("Figure 2. Regression coefficients from generalized linear models of mating success\n",
 #                                       size = 20, face = "bold",
 #                                       hjust = 0,
 #                                       x = 0.01),
 #                       bottom = text_grob("\nVariables labelled (S) have been centered at the mean and standarized by 2 SD Base level of race/ethnicity is Mexican American.",
 #                                          size = 12))

@@

```{r immune, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of predictors of immune investment (WBCC) from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standardized by 2 SD."}
Figure3 <- forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  theme_minimal(17) +
 # geom_pointrange(size = 2, position = position_dodge(width = .8)) +
 # labs(title = "White blood cell count") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))

@@

```{r dietary, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of predictors of dietary energy intake (kcals) from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standardized by 2 SD."}
Figure4 <- forestplot(
  m_energy,
  m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  theme_minimal(17) +
  #geom_pointrange(size = 2, position = position_dodge(width = .8)) +
  #labs(title = "Dietary energy intake") + 
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "Caroline B. Smith and Edward H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
# csl: apa.csl
# bibliography: regrep.bib
---

@@

source('analysis.R')
```
EHB Registered Report

@@

Figure1 <- forestplot(
  m_agefirst,
  m_lifetime,
  m_pastyear,
  m_partnered,
  intercept = F,
  facet = F,
  dodgewidth = .5,
  modelnames = mnames1,
  varnames = vnames, 
  size = 1.2, 
  linewidth = 1,
  ddf = Inf
) + theme_minimal(17) +
#  geom_pointrange(size = 1.2, position = position_dodge(width = .5)) +
#  labs(title = "Figure 1. Baseline Models: Regression coefficients from generalized linear models", color = "Model") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
# 
# 
# annotate_figure(fig1,
#                            top = text_grob("Figure 1. Baseline Models: Regression coefficients from generalized linear models\n",
#                                            size = 20, face = "bold",
#                                            hjust = 0,
#                                            x = 0.01),
#                            bottom = text_grob("Variables labelled (S) have been centered at the mean and standarized by 2 SD",
#                                               size = 12))

@@

# "Partnered x Strength (S)"

forestplot_custom <- function(m1, m2, m3, m4, nm, title, y_axis=F){
  d <- forestplot(
    m1, m2, m3, m4,
    intercept = F,
    modelnames = mnames, 
    varnames = vnames,
    ddf = Inf,
    draw = F
  )

  if (!is.null(nm)){
    for (n in nm){
      d <- bind_rows(
        d,
        tibble(
          Model = c('Health', 'Hormone', 'Physical Activity', 'Socioeconomic'),
          term = factor(rep(n, 4)),
          estimate = c(NA, NA, NA, NA),
          std.error = c(NA, NA, NA, NA),
          statistic = c(NA, NA, NA, NA),
          p.value = c(NA, NA, NA, NA),
          conf.low = c(NA, NA, NA, NA),
          conf.high = c(NA, NA, NA, NA)
        )
      )
    }

  }
  p <- 
    d %>% 
    ggplot(aes(estimate, term, xmin=conf.low, xmax=conf.high, colour=Model, shape=Model)) + 
    geom_pointrange(size = 0.7, linewidth = 0.7, position = position_dodge(width = 0.8)) +
    geom_vline(xintercept=0, linetype='longdash') +
    labs(title = title, y='', x='Estimate (95% CI)', ) +
    theme_minimal() +
    theme(plot.title = element_text(size = 11))

    if (!y_axis){
      p <- p + theme(axis.text.y = element_blank())
    }
  return(p)
}

fig1 <- forestplot_custom(
  msoc2,mheal2, mphys2, mhor2,
  NULL, 
  "Past Year Number of Sexual Partners",
  y_axis = T
)

fig2 <- forestplot_custom(
  msoc1, mheal1, mphys1, mhor1, 
  'Partnered x Strength (S)', 
  "Lifetime Number of Sexual Partners"
)

fig3 <- forestplot_custom(
  msoc3, mheal3, mphys3, mhor3,
  "Partnered x Strength (S)", 
  "Age at First Sex"
)

fig4 <- forestplot_custom(
  msoc4, mheal4, mphys4, mhor4,
  c("Partnered", "Partnered x Strength (S)"), 
  "Currently Partnered"
)

@@

@@

```{r immune, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of predictors of immune investment (WBCC) from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standardized by 2 SD."}
Figure3 <- forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames,
  ddf = Inf) +
  theme_minimal(17) +
 # geom_pointrange(size = 2, position = position_dodge(width = .8)) +
 # labs(title = "White blood cell count") +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))

@@

```{r dietary, fig.width = 12, fig.height = 8, fig.cap = "Coefficient plot of predictors of dietary energy intake (kcals) from generalized linear models (Pilot). Variables labelled (S) have been centered at the mean and standardized by 2 SD."}
Figure4 <- forestplot(
  m_energy,
  m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames,
  ddf = Inf) +
  theme_minimal(17) +
  #geom_pointrange(size = 2, position = position_dodge(width = .8)) +
  #labs(title = "Dietary energy intake") + 
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))
  # labs(title = "Figure.3 Regression coefficients from generalized linear model of immune investment.",
  #      subtitle = "White Blood Cell Count",
  #      caption = "Variables with (S) have been standarized by 2 SD.") +
  # guides(colour = guide_legend(reverse = T))
